Learning Discrete-valued Bayesian Networks from Mixed Data

### 2015-11-22 probability_plot_old/graph_wine_exp1_distr.tex
Change all plots from probability to probability density

\begin{tikzpicture}
  \begin{groupplot}[
	  	group style={group size=2 by 1,horizontal sep=1cm,
  		}, 
  		width = 1/2*\textwidth - 1cm,
  		height = 6 cm ]%,xmin=0,ymin=0,height=4cm,width=5cm,no markers]
  \nextgroupplot[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			ylabel=$K$,
			xlabel=$E$,
			%colorbar,
    %every colorbar/.append style={height=
    %    2*\pgfkeysvalueof{/pgfplots/parent axis height}+
     %   \pgfkeysvalueof{/pgfplots/group/vertical sep}},
		    point meta min=0, point meta max=0.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);}
			%colorbar style={
			%        ytick={0,0.05,...,0.51},
			%        yticklabel style={
			%            text width=2.5em,
			%            align=right,
			%            /pgf/number format/.cd,
			%                fixed,
			%                fixed zerofill
			%        }
			%    }
			]

@@

    \nextgroupplot[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=$E$,
			%ylabel=K,
			colorbar,
			point meta min=0, point meta max=0.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.05,...,0.51},
			        yticklabel style={
			            text width=1.5em,
			            align=right,
			           /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

>>>>

\begin{tikzpicture}
  \begin{groupplot}[
	  	group style={group size=2 by 1,horizontal sep=1.5em,
  		},
  		width = 1/2*\textwidth - 1em,
  		height = 6 cm ]%,xmin=0,ymin=0,height=4cm,width=5cm,no markers]
  \nextgroupplot[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			ylabel=$K$,
			xlabel=$E$,
			%colorbar,
    %every colorbar/.append style={height=
    %    2*\pgfkeysvalueof{/pgfplots/parent axis height}+
     %   \pgfkeysvalueof{/pgfplots/group/vertical sep}},
		    point meta min=0, point meta max=0.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);}
			%colorbar style={
			%        ytick={0,0.05,...,0.51},
			%        yticklabel style={
			%            text width=2.5em,
			%            align=right,
			%            /pgf/number format/.cd,
			%                fixed,
			%                fixed zerofill
			%        }
			%    }
			]

@@

    \nextgroupplot[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=$E$,
			%ylabel=K,
			colorbar,
			point meta min=0, point meta max=0.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.05,...,0.51},
			        ylabel=probability density,
			        y label style={at={(axis description cs:6.0,0.5)},rotate=180,anchor=north},
			        yticklabel style={
			            text width=1.5em,
			            align=right,
			           /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]
